### 2015-06-01 writing/SNLI paper/entailment_eval.tex
Gah; another typo

%
% EOP
%
\paragraph{Excitement Open Platform}
% what is EOP
The Excitement Open Platform is a tool to quickly develop NLI systems
  while sharing components such as common lexical resources and 
  evaluation sets.
We evaluate against two algorithms included in the distribution,
  and also evaluated in \newcite{magnini2014excitement}.
These are: 
  a simple edit-distance based algorithm; and
  a classifier-based algorithm.
%  (3) an algorithm based around tree transformations.

>>>>

%
% EOP
%
\paragraph{Excitement Open Platform}
% what is EOP
The Excitement Open Platform is a tool to quickly develop NLI systems
  while sharing components such as common lexical resources and 
  evaluation sets.
We evaluate against two algorithms included in the distribution:
%  and also evaluated in \newcite{magnini2014excitement}.
%These are: 
  a simple edit-distance based algorithm and
  a classifier-based algorithm.
%  (3) an algorithm based around tree transformations.
